onsetsync: An R Package for Onset Synchrony Analysis

### 2023-09-14 paper/paper.Rmd
suppressed installation message

```{r secret_load, eval=TRUE, echo=FALSE}
devtools::install_github("tuomaseerola/onsetsync@R1",force = TRUE)
#library(onsetsync)
ver <- packageVersion('onsetsync')
```

@@

```{r availability,eval=FALSE}
library(devtools)
devtools::install_github("tuomaseerola/onsetsync@R1",force = TRUE")
library(onsetsync)
```

>>>>

```{r secret_load, eval=TRUE, echo=FALSE,message=FALSE,warning=FALSE}
devtools::install_github("tuomaseerola/onsetsync@R1",force = TRUE,quiet=TRUE)
library(onsetsync)
ver <- packageVersion('onsetsync')
```

@@

```{r availability,eval=FALSE,message=FALSE,warning=FALSE}
library(devtools)
devtools::install_github("tuomaseerola/onsetsync")
library(onsetsync)
```
